A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-09-22 manuscript.Rmd
remove sloppy wording in definition closes #64
consistent slashes in make example

In this tutorial, we describe a workflow to ensure long-term and cross-platform reproducibility of data analyses in R [@baseR]. Reproducibility is the ability to draw an identical conclusion from the same statistical analysis and the same data. For us,  statistical results are only reproducible if their generating, computational workflow is reported fully and transparently, and remains sustainably available, such that the workflow can be re-run by a different person or later in time, and that the results will be identical to the ones initially reported [@turingway2020; @herouxCompatibleReproducibilityTaxonomy2018; @claerboutElectronicDocumentsGive1992]. The need to ensure reproducibility directly follows from commonly accepted rules of good scientific practice [such as the guidelines of the German Research Foundation; @dfg2019]. Ensuring reproducibility is a prerequisite for replicability (the ability to reach a similar conclusion from the same analysis and _new_ data), and a means to increase the trustworthiness of empirical results [@epskamp2019rep]. Transparency and accessibility are central scientific values, and open, reproducible projects will increase the efficiency and veracity of knowledge accumulation [@nosek2012scientific].

@@

The first line after the comment is the first (default) target called 'all', which depends on manuscript.pdf, which itself is a target. If Make is called without an argument, the first target is built. To create `manuscript.pdf` (the second target in the file), the file `manuscript.Rmd` needs to be rendered, which depends on `data/iris_prepped.csv`. This dependency is itself a target (the third target in the file). To create `data/iris_prepped.csv`, `R/prepare_data.R` and `data/iris.csv` are needed. If you type `make manuscript.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/iris_prepped.csv` does not exist, Make creates it by executing the third target. Also, if one of the dependencies of a target is newer than the target itself, Make updates everything that directly or indirectly depends on the target. Here, if `data\iris.csv` is newer than `data\iris_prepped.csv`, Make will attempt to recreate `data\iris_prepped.csv` first and then `manuscript.pdf`. If there is a dependency missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which creates the entire project. Subsequently, the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure \@ref(fig:buildpane-rstudio)).

>>>>

In this tutorial, we describe a workflow to ensure long-term and cross-platform reproducibility of data analyses in R [@baseR]. Reproducibility is the ability to draw identical results from the same statistical analysis and the same data. For us,  statistical results are only reproducible if their generating, computational workflow is reported fully and transparently, and remains sustainably available, such that the workflow can be re-run by a different person or later in time, and that the results will be identical to the ones initially reported [@turingway2020; @herouxCompatibleReproducibilityTaxonomy2018; @claerboutElectronicDocumentsGive1992]. The need to ensure reproducibility directly follows from commonly accepted rules of good scientific practice [such as the guidelines of the German Research Foundation; @dfg2019]. Ensuring reproducibility is a prerequisite for replicability (the ability to reach a similar conclusion from the same analysis and _new_ data), and a means to increase the trustworthiness of empirical results [@epskamp2019rep]. Transparency and accessibility are central scientific values, and open, reproducible projects will increase the efficiency and veracity of knowledge accumulation [@nosek2012scientific].

@@

The first line after the comment is the first (default) target called 'all', which depends on manuscript.pdf, which itself is a target. If Make is called without an argument, the first target is built. To create `manuscript.pdf` (the second target in the file), the file `manuscript.Rmd` needs to be rendered, which depends on `data/iris_prepped.csv`. This dependency is itself a target (the third target in the file). To create `data/iris_prepped.csv`, `R/prepare_data.R` and `data/iris.csv` are needed. If you type `make manuscript.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/iris_prepped.csv` does not exist, Make creates it by executing the third target. Also, if one of the dependencies of a target is newer than the target itself, Make updates everything that directly or indirectly depends on the target. Here, if `data/iris.csv` is newer than `data/iris_prepped.csv`, Make will attempt to recreate `data/iris_prepped.csv` first and then `manuscript.pdf`. If there is a dependency missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which creates the entire project. Subsequently, the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure \@ref(fig:buildpane-rstudio)).
